\mytitle

### 2023-05-05 chapters/intro.tex
jitsynth part of intro

\section{Synthesis for In-Kernel Compilers}
% TODO
% JitSynth: break up into minicompilers (TODO)
% JitSynth: design metasketch to describe common minicompiler patterns (TODO)

@@

\section{Contributions}

>>>>

\section{Synthesis for In-Kernel JIT Compilers}
Modern operating systems have become increasingly extensible and customizable.
One way these systems enable customization is by
allowing users to submit custom code for kernel execution
written in an \textit{in-kernel DSL}.
Initially designed for network packet filtering, 
in-kernel DSLs like eBPF \todo{cite} enable kernel extentions
such as performance monitoring, load balancing, and intrusion detection.\todo{cite https://ebpf.io/case-studies/}
For performance reasons, operating systems use just-in-time (JIT) compilers
to execute in-kernel DSL programs.
However,
% as mentioned previously, % TODO?
these JIT compilers can be the source of major kernel bugs.\todo{cite}
Moreover, writing JIT compilers can pose a substantial effort to developers,
requiring on the order of thousands of lines of code.\todo{cite}

In \cref{c:jitsynth}, I present \jitsynth, a program synthesis tool that
automatically generates JIT compilers for in-kernel DSLs
given a specification of the source and target language.
Existing work has demonstrated how the correctness of JIT compilers
can be proven manually\todo{cite},
but the effort of such proofs is highly non-trivial.
By synthesizing JIT compilers, developers both avoid the burden of implementing
such systems \textit{and} can guarantee correctness
without requiring intensive proofs.

% JitSynth: break up into minicompilers (TODO)
In order to synthesize such massive and complex systems,
\jitsynth considers the synthesis problem as one over per-instruction compilers
between \textit{abstract register machines} --- an abstraction over
in-kernel DSLs and other low-level languages introduced in \cref{c:jitsynth}.
\jitsynth decomposes the synthesis problem for per-instruction compilers
into multiple synthesis tasks for \textit{minicompilers}
that translate only one source instruction.% TODO include this line?
% JitSynth: design metasketch to describe common minicompiler patterns (TODO)
To prune and prioritize the search space for minicompilers,
\jitsynth takes advantage of a novel \textit{compiler metasketch}
that enables the efficient exploration of candidate minicompilers
using off-the-shelf satisfiability solvers.
With \jitsynth, we have synthesized three JIT compilers:
one from eBPF to RISC-V,
one from classic BPF to eBPF,
and one from libseccomp to eBPF.
Moreover, we have confirmed that the synthesized eBPF to RISC-V compiler
lacks bugs found in the existing Linux compiler.

@@

\section{Contributions}
The remainder of this dissertation is broken into two chapters.
The first presents \jitsynth, a tool for synthesizing just-in-time compilers for
in-kernel DSLs.
k
